The abundance of Bullet Groups in $\Lambda$CDM

### 2014-03-08 paper/ms.tex
new abstract

\title{The abundance of Bullet Groups in $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$
  and T. Verdugo$^3$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela}

@@

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 \hkpc is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{New_figures/figure_2.eps}
\end{center}
\caption{
  Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continuous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures_eps/figure_4_VcircsubVcirchalo_300kms_700kms.eps} 
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacement}}
\label{fig:velocities}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_4_300kms_700kms.eps}
\end{center}
\caption{x}
\label{fig:geometry}
\end{figure*}

@@

\begin{figure}
\begin{center}
%\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
\end{center}
\caption{Integrated probability distribution for the estimated
  baryonic displacements in the group and cluster samples at all redshifts.}
\label{fig:baryonic_displacements}
\end{figure}

>>>>

\title{The abundance of Bullet Groups in $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
  T. Verdugo$^3$, G. Foex$^4$ and V. Motta$^4$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela\\
  $^4$ Departamento de F\'isica y Astronom\'ia, Universidad de
  Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
  2360102, Chile  
}

@@

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that 5\% to 25\% of the dark matter systems
with circular velocities in the range $300\kms$ to $700\kms$ show
multimodal morphologies with displacements between the dark matter
clumps equal or larger to $\sim 400$\hkpc, which corresponds to the
observational constraint the object SL2S J08544-0121 located at
$z=0.35$. 
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_2.eps}
\end{center}
\caption{
  Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continuous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_5.eps} 
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_3.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacement}}
\label{fig:velocities}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_4.eps}
\end{center}
\caption{x}
\label{fig:geometry}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figures_eps/figure_7.eps}
\end{center}
\caption{Integrated probability distribution for the estimated
  baryonic displacements in the group and cluster samples at all redshifts.}
\label{fig:baryonic_displacements}
\end{figure}
